 ---
<h2 style="color: blue;font size=16"> Field Report</h2> 
 --------
<br>

<h3 style="font size=12">
National Coral Reef Monitoring Program - Climate Monitoring
Coral Reef Conservation Program &amp; Ocean Acidification Program
Field report from Dry Tortugas Research Cruise - </h3>

<br>

<h4 style="font size=8">
Atlantic Oceanographic &amp; Meteorological Laboratory
National Oceanic Atmospheric Administration
Nicole Besemer (July 2021) </h4>

#title: "DRTO Field Report"
#author: "Nicole Besemer, Ana Palacio and Ian Enochs"
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    df_print: paged
    theme: united
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(plotly)
library(scales)
library(ggpubr)
library(RColorBrewer)
library(scales)
library(openair)
library(magick)
library(ggplot2)
```


## Summary

Work under the National Coral Reef Monitoring Plan (NCRMP) was completed in the Dry Tortugas National Park over the course of five days from June 25th through June 29th, 2021. Work was conducting aboard the R/V ANGARI (ANGARI Foundation) and conducted utilizing permits DRTO-2020-SCI-0010 and DRTO-2020-SCI-0011. During these operations, the following deliverables were successfully met:

* Recovery and redeployment (replacement) of all four Subsurface Temperature Recorders (STRs) at the one, five, 15, and 25 meter depths

* Recovery and redeployment (replacement) of all five Calcification Accretion Units (CAUs) and all five Bioerosion Monitoring Units (BMUs), an additional 5 BMUs were installed

*	Collection of 72-hours of Class II discrete water samples via Subsurface Automatic Samplers (SAS) at three hour intervals (total of 22 samples taken – two samples unsuccessfully deployed)

*	Completion of benthic, bioeroder, and parrotfish surveys (Perry Surveys) at all six transect sites

*	Completion of photomosaics at all six survey transect sites

*	Deployment of SeaFET pH logger, Tiltmeter and EcoPAR coinciding with all 72 hours of Class II water sampling data


*(I want a better picture but this is placeholder for the moment)
* Cool, when you have the final one you need to meve it inside the project folder so the path works for both of us (I cannot access your desktop :) ). Ana



**Personnel**: Nicole Besemer (Chief Scientist), Graham Kolodziej, Nathan Formel, Anderson Mayfield and Patrick Kiel. 

**Total working dives logged**: 63

------

## Prelimanary Data

### Temperature Data

Summary plots from all 4 Subsurface Temperature Recorders (STRs) collected at our study site locations. The 1m, 5m, and 15m collected data for the full deployment. The 25m STR stopped collecting on Febuary 7th 2020.


```{r get Temp, include=FALSE}

# 1. Import all processed temperature data and add depht: 

## This code allow us to chose each file "manually". We can get the file names automatically (as in Mike's code), both have advantages and disadvantages. 

  # 1m data
  str01 <- read_csv('Data/DRTOSTRs/DRTO_west_01m_sn7774_tag3094_pulaski-shoal_2018-07-11_2021-06-27_processed.csv', col_types = cols())
  str01$Depth<-"1m"
  # head(str01)
  
  # 5m data
  str05 <- read_csv('Data/DRTOSTRs/DRTO_west_05m_sn8621_tag3093_white-shoal_2018-07-11_2021-06-26_processed.csv', col_types = cols())
  str05$Depth<-"5m"
  #head(str05)
  
  # 15m data
  str15 <- read_csv('Data/DRTOSTRs/DRTO_west_15m_sn7769_tag3092_bird-key-reef_2018-07-11_2021-06-27_processed.csv',col_types = cols())
  str15$Depth<-"15m"
  #head(str15)
  
  # 20m data
  str20 <- read_csv('Data/DRTOSTRs/DRTO_west_25m_sn7784_tag3091_black-coral-rock_2018-07-12_2020-02-07_processed.csv',col_types = cols())
  str20$Depth<-"20m"
  head(str20)

# 2. Bind all data and order depth  
  str_all<-rbind(str01, str05, str15, str20)
  str_all$Depth<-factor(str_all$Depth, levels = c("1m", "5m", "15m", "20m"))

```

```{r Tempvariables, include=FALSE}
# 3. Define limits for temperature and time (if we want to follow Mike's, this is not really needed with my way of plotting)
  globalMinDate <- min(str_all$UTCDateTime)
  globalMinTemp <- min(str_all$Temperature)
  globalMaxDate <- max(str_all$UTCDateTime)
  globalMaxTemp <- max(str_all$Temperature)

# 4. Define breaks in the x axis
  if ((globalMaxDate-globalMinDate) > 365.25) {
    xWidth <- "4 months"
  } else {
    xWidth <- "1 month"
  }

```

Plot option 1: need colors 

```{r plot temperature option 1, echo=FALSE,fig.width = 8.5,fig.height = 4.5}

# This is one option using colors to plot all temp data in the same plot (easy to see differences). If that is too much we can facet the data (opcion 2)

plot<-ggplot(data = str_all) +
      geom_line(aes(x = ymd_hms(UTCDateTime), 
                    y = Temperature, colour=Depth),
                size=0.4) +
  
  theme_bw() +
  theme(axis.title.x = element_blank(),
        legend.position = c(0.5, 0.05) ,
        legend.direction = "horizontal" ,
        plot.margin = unit(c(5.5, 15, 5.5, 5.5), "points")) +
      
  scale_x_datetime(breaks = breaks_width(xWidth),
                       labels = date_format("%m/%Y"),
                       limits = c(globalMinDate, globalMaxDate)) +
  scale_y_continuous(limits = c(globalMinTemp, globalMaxTemp)) +
      ylab(expression(atop(
        paste("Temperature (", degree, "C)")
      ))) 
      
    
box <- ggplot(data = str_all) +
      geom_boxplot(aes(x = "", y = Temperature, fill=Depth)) +
      theme_bw() +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            legend.position = "none")+
      scale_y_continuous(limits = c(globalMinTemp, globalMaxTemp))
    
Figure1 <- ggarrange(plot, box, widths = c(8, 2))
Figure1    
```

Plot 1 option 2

```{r plot temperature option 2, echo=FALSE,fig.width =8.5,fig.height = 11}

# facet the data (opcion 2)

plot<-ggplot(data = str_all) +
      geom_line(aes(x = ymd_hms(UTCDateTime), 
                    y = Temperature), 
                colour="dodgerblue") +
  
  theme_bw() +
  theme(axis.title.x = element_blank(),
        legend.position = c(0.5, 0.05) ,
        legend.direction = "horizontal" ,
        plot.margin = unit(c(5.5, 15, 5.5, 5.5), "points")) +
      
  scale_x_datetime(breaks = breaks_width(xWidth),
                       labels = date_format("%m/%Y"),
                       limits = c(globalMinDate, globalMaxDate)) +
  scale_y_continuous(limits = c(globalMinTemp, globalMaxTemp)) +
      ylab(expression(atop(
        paste("Temperature (", degree, "C)")
      ))) +
  facet_grid(Depth~.)
      
    
box <- ggplot(data = str_all) +
      geom_boxplot(aes(x = "", y = Temperature), fill='dodgerblue') +
      theme_bw() +
      theme(axis.title.x = element_blank(),
            axis.title.y = element_blank(),
            legend.position = "none")+
      scale_y_continuous(limits = c(globalMinTemp, globalMaxTemp))+
  facet_grid(Depth~.)
    
Figure1b <- ggarrange(plot, box, widths = c(8, 2))
Figure1b   

```

<font size="2"> **Figure 1:** Temperature bla bla bla at 1 m (Pulaski Shoal Lighthouse), 5m (white-shoal15m), 15m (Bird Key Reef) and 25 m (Black Coral Rock)</font>
 
 
 Plot 1 option 2 with title  

```{r plot temperature option 2b, echo=FALSE,fig.width =8.5,fig.height = 11}
Figure1b_Title = annotate_figure(Figure1b, top = "Add Title here if you want")
Figure1b_Title

```


Describe temperature results here 

-----

### Current Data

Tiltmeters are used to collect data on current movement. The below data was collected from a Lowell Instruments tilt meter deployed from June 25th to June 28th:

```{r tiltmeter data, echo=FALSE}
fileAny <- "Data/2102061_DRTO-2021-06_(0)_Current.csv"

# hardcoded limits for this DRTO file are
# ymd_hms("2021/06/25 18:30:00") and ymd_hms("2021/06/28 19:45:00")
# (future enhancement: incorporate Hannah Barkley's dataset trimming code;
#  also, eliminate all the hardcoding below and calculate from data)

dataAny <- read.csv(fileAny, header = TRUE)
dataAny$date = ymd_hms(paste0(dataAny$Date, dataAny$Time), tz = "UTC")
dataAny <- dataAny[, c("date","Speed..cm.s.","Heading..degrees.")]
colnames(dataAny) <- c("date","ws","wd")
dataAny$dateEDT<-NA
dataAny <- subset(dataAny, date >= ymd_hms("2021/06/25 18:30:00") & date <= ymd_hms("2021/06/28 19:45:00"))
dataAny$dateEDT <- lubridate::with_tz(dataAny$date, "America/New_York")

# 2021/07/09 working up more tiltmeter graphs completely in R
# (not just openair's windRose plot, which was suggested by Ian originally)

```

```{r tiltmeter plot, echo=FALSE,fig.width = 12, fig.height = 3.5}

# line plot (Current Speed)
ggplot(data = dataAny) +
  geom_line(aes(x = dateEDT, y = ws), col = 'dodgerblue') +
  theme_bw() +
  theme(plot.margin = unit(c(5.5, 15, 5.5, 5.5), "points")) +
  scale_x_datetime(breaks = date_breaks("8 hours"),
                   labels = date_format("%m/%d\n%H:%M"),
                   limits = c(ymd_hms("2021/06/25 16:00:00"),ymd_hms("2021/06/28 22:00:00")),
                   expand=c(0,0)) +
  ylab(expression(atop("Current Speed (cm/s)"))) +
  xlab(expression(atop("Date and Time (EDT)"))) +
  scale_y_continuous(expand=c(0,0),limits=c(0,12))

```

<font size="2"> **Figure 2:** Current bla bla bla </font>

Describe current results here 

-----


### Light Data

instert blurb about EcoPar

```{r ecopar data, echo =FALSE}

PAR <- read_csv('Data/DRTO_EcoPAR07062021.csv',col_types = cols()) %>%
          mutate(DateTime = mdy_hms(paste(Date, Time))) %>%
          select(DateTime, `PAR (CALC)`) %>%
          drop_na() %>%
          mutate(interval = 0:(nrow(.)-1) %/% 10) %>%
          group_by(interval) %>%
          summarise(DateTime = mean(DateTime),
                    PAR = mean(`PAR (CALC)`),
                    sd = sd(`PAR (CALC)`)) %>%
        select(-interval) %>%

  #manual start/stop time of monitoring
  filter(DateTime >= as.POSIXct('2021-06-25 18:35:00', tz='UTC') &
         DateTime <= as.POSIXct('2021-06-28 19:45:00', tz='UTC')) %>%
  mutate(DateTime = with_tz(DateTime, 'America/New_York'))
```


```{r ecopar plot, echo=FALSE, fig.width = 12,fig.height = 3.5}
PAR %>%
  ggplot(aes(x=DateTime, y=PAR)) +
  geom_line(color = "dodgerblue", size=1) + 
  theme_bw() +
  labs(title = "PAR of NCRMP-DRTO Plots Jun 26 - 28 '21",
       y = expression(paste("PAR (",mu,"mol photons m"^-2,"s"^-1,")")),
       x = "Time of Day (EDT)") +
  scale_x_datetime(date_breaks = "6 hour",
                   date_minor_breaks = "3 hour",
                   date_labels = "%H:%M")
```

<font size="2"> **Figure 3:**  bla bla bla </font>

Describe light results here 

-----

### pH data

SeaBird SeaFETs are used to collect pH data at our Bird Key Reef Site. The below data was deployed from June 25th to June 28th:

```{r}
# There is also /DRTO_SeaFET07062021(1).csv, what isthe difference?

pH <- read_csv('Data/DRTO_SeaFET07062021.csv',col_types = cols()) %>%
    select(DateTime = `DateTime (UTC+00:00)`,
           pH = `Internal pH (pH)`,
           Temperature = `pH Temperature (Celsius)`) %>%
    mutate(DateTime = parse_date_time(DateTime, '%m/%d/%Y %H:%M')) %>%
    #manual start/stop time of monitoring
   filter(DateTime >= as.POSIXct('2021-06-25 18:35:00', tz='UTC') &
         DateTime <= as.POSIXct('2021-06-28 19:45:00', tz='UTC')) %>%
  mutate(DateTime = with_tz(DateTime, 'America/New_York'))
```


```{r SeaFET data, echo=FALSE, fig.width = 12, fig.height = 3.5}
pH %>%
  ggplot(aes(x=DateTime, y=pH)) +
  geom_line(color = "red", size=1) + 
  theme_bw() +
  labs(title = "pH of NCRMP-DRTO Plots Jun 26 - 28 '21",
       y = "pH",
       x = "Time of Day (EDT)") +
  scale_x_datetime(date_breaks = "6 hour",
                   date_minor_breaks = "3 hour",
                   date_labels = "%H:%M")

#pH and temp combined -----
pH$Temp.adj <- (pH$Temperature * 0.1099) + 4.8371
ggplot(data = pH) +
  annotate("rect",
          xmin = seq.POSIXt(as.POSIXct('2021-06-25 19:00:00', tz='EST'),
                         by = "day", length.out = 3),
          xmax = seq.POSIXt(as.POSIXct('2021-06-26 08:00:00', tz='EST'),
                         by = "day", length.out = 3),
          ymin = -Inf, ymax = Inf,
          fill="grey", alpha=0.5) +
  geom_line(aes(x=DateTime, y=pH, color = "pH"),
            size=1) +
  geom_line(aes(x=DateTime, y=Temp.adj, color = "Temperature"),
            size=0.7, alpha = 0.5) +
  labs(title = "NCRMP-DRTO Data Jun 25 - 28 '21",
       y = "pH",
       x = "Time of Day (EDT)") +
  scale_y_continuous(limits = c(7.925,7.985), sec.axis = sec_axis(~(.-4.8371)/0.1099)) +
  scale_x_datetime(date_breaks = "6 hour",
                   date_minor_breaks = "3 hour",
                   date_labels = "%H:%M") +
  annotate("text",
           label = expression(paste("Temperature (",degree,"C)")),
           angle=90,
           x = max(pH$DateTime+(3600*10)),
           y = 7.95) + 
  coord_cartesian(ylim = c(7.925,7.985),
                    xlim = c(min(pH$DateTime),max(pH$DateTime)),
                    clip = 'off',
                    expand = T) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.margin = unit(c(1,3,1,1), "lines"),
        legend.position = "bottom") +
  annotate("text",
          label = paste("Jun", 25:28),
          x = seq.POSIXt(as.POSIXct('2021-06-25 13:30:00', tz='EST'),
                         by = "day", length.out = 4),
          y = 7.985)
```

<font size="2"> **Figure 4:**  bla bla bla </font>

Describe pH results here 


